---
title: "HW_02"
author: "Yuke Han"
date: "2024-02-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1:
```{r}
library(tidyverse)
dt <- tribble(
  ~x, ~y, ~w, ~z,
  210, 300, 220, 180,
  102, 100, 119, 187,
  176, 175, 188, 173,
  87, 95, 91, 94,
  202, 210, 234, 218,
  110, 122, 131, 128
)
dt
```

### 1_a:
• Use and show a map function to find the “mean” of each column of the dt data table

```{r}
mean_dt <- map(dt, mean)
mean_dt
```

### 1_b:
• Use and show a map function to find the “standard deviation” of each column of the dt data table.

```{r}
sd_dt <- map(dt, ~sd(.x, na.rm = TRUE))
sd_dt
```

### 1_c:
• Use and show a map function that will calculate the “square root” of each value of each column of the data table dt.

```{r}
sqrt_dt <- map_df(dt, sqrt)
sqrt_dt
```

### 1_d:
• Use R code to find the “mean”, “max”, “1st Quartile”, “3rd Quartile”, “Median”, and “Min” for each column of the dt data table. (Hint: You do not have to use a map function)

```{r}
summary_stats <- dt %>%
  summarise(across(everything(), list(mean = ~mean(.x, na.rm = TRUE),
                                      max = ~max(.x, na.rm = TRUE),
                                      Q1 = ~quantile(.x, 0.25, na.rm = TRUE),
                                      median = ~median(.x, na.rm = TRUE),
                                      Q3 = ~quantile(.x, 0.75, na.rm = TRUE),
                                      min = ~min(.x, na.rm = TRUE)))) %>%
  pivot_longer(cols = everything(), names_to = c(".value", "statistic"), names_pattern = "(.*)_(.*)")
print(summary_stats)
```


## Problem 2:
Write a function that uses a for loop that, for each iteration, randomly draws 5 observations from an exponential distribution with “rate” parameter 1 (use rexp()) and calculates its “mean”. It should do this 10,000 times. Choose an appropriate plot to plot the distribution of “means”.

```{r}
simulate_means <- function(n, size, rate) {
  means <- numeric(n) 
  for (i in 1:n) {
    sample <- rexp(size, rate)
    means[i] <- mean(sample)
  }
  return(means)
}

set.seed(123)
means <- simulate_means(10000, 5, 1)
hist(means, breaks = 50, main = "Distribution of Means", xlab = "Means", col = 'skyblue')

```

### 2_a:
• Repeat part 1 by using a map_*() function.

```{r}
set.seed(123)
means_map <- map_dbl(1:10000, ~mean(rexp(5, 1)))
hist(means_map, breaks = 50, main = "Distribution of Means using map", xlab = "Means", col = 'green')

```

### 2_b:
• Repeat part 1 by using the replicate() function.

```{r}
set.seed(123)
means_replicate <- replicate(10000, mean(rexp(5, rate = 1)))
hist(means_replicate, breaks = 50, main = "Distribution of Means using replicate", xlab = "Means", col = 'red')
```

2_c:
• Use a another for loop that will print out plots for sample sizes of 5, 10, and 20 observations (instead of just 5).

```{r}
set.seed(123)
sample_sizes <- c(5, 10, 20)
for (size in sample_sizes) {
  means <- replicate(10000, mean(rexp(size, rate = 1)))
  hist(means, breaks = 50, main = paste("Distribution of Means for Sample Size", size), xlab = "Means", col = 'brown')
}
```


## Problem 3:
• Use and show R coding to calculate the “standard deviation” for each variable of the data table mtcars using the “Special For Loop Method”.

```{r}
data(mtcars)
output <- vector("double", ncol(mtcars))
for (i in seq_along(mtcars)) {
  output[[i]] <- sd(mtcars[[i]], na.rm = TRUE)
}
names(output) <- names(mtcars)
print(output)
```


